Figures for conference paper

### 2019-04-30 conference figures.Rmd

      node [fontname = Helvetica, shape = rectangle]

      subgraph cluster_input {
      label = '';
      style = filled;
		  color = white;

      subgraph cluster_input_data {
      label = 'Data';
      style = filled;
		  color = lightgrey;
		  node [style = filled, color = black, fillcolor = white, shape = cylinder];
      CD [label = 'Course Data']
      SD [label = 'Student Data']
      }

      subgraph cluster_input_user {
      label = 'User Input';
      style = filled;
		  color = coral;
		  node [style = filled, color = black, fillcolor = white];
      ID [label = 'Student ID']
      KW [label = 'Selected Key Words']
      CS [label = 'Selected Courses']
      }

@@

      subgraph cluster_inter_first{
      label = '';
      style = filled;
		  color = white;
      AP [label = 'Academic Performance']
      TR [label = 'Student´s Transcript']
      TE [label = 'Topic Expertise']
      }

      subgraph cluster_inter_last{
      label = '';
      style = filled;
		  color = white;
      GP [label = 'Grade Prediction']
      AI [label = 'Student´s Academic Interests']
      }

      # Ouput
      subgraph cluster_ouput {
      label = 'System Output';
      style = filled;
		  color = lightCyan;
		  node [style = filled, color = black, fillcolor = white];
      rank = same;
      SUG [label = 'Course Suggestions']
      WAR [label = 'Warnings']
      PRE [label = 'Preparatory Coursework']
      }

      # Intermediate nodes
      node [color = black]
      TM [label = 'Topic Model']
      PM [label = 'Predictive Models']

      # Invisible node
      node [shape = circle, width = .01, height = .01, label = '']
      x1 x2 x3

@@

      SD -> AP;
      {SD, TM} -> TE;
      {TR, KW} -> AI;
      {ID, SD} -> TR;
      {PM, CS, TR} -> GP;
      GP -> WAR;
		  WAR -> PRE;

      edge[label = 'LDA', decorate = TRUE]
      CD -> TM;

      edge[label = '']
      {AP, TE} -> x1 [arrowhead = none]
      edge[label = ' Lasso', decorate = TRUE]
      x1 -> PM;

      edge[label = '']
      {TM, AI} -> x2 [arrowhead = none]
      edge[label = 'KL distance', decorate = TRUE]
      x2 -> SUG;

      edge[label = '']
      {TM, PM} -> x3 [arrowhead = none]
      edge[label = 'KL distance', decorate = TRUE]
      x3 -> PRE;

@@

  labs(title = "Model Selection", subtitle = "The maximum-likelihood model has 80 topics", x = "Number of Topics", y = "Log-Likelihood") +

>>>>

      fontname = Helvetica
      size = 15

      node [fontname = Helvetica, shape = rectangle, style = filled, color = black, fillcolor = white]

      edge [fontname = Helvetica, decorate = TRUE]

      subgraph cluster_data {
      label = 'Data';
      style = filled;
		  color = lightgrey;
		  node [shape = cylinder];
      CD [label = 'Course Data']
      SD [label = 'Student Data']
      }

      subgraph cluster_input_user {
      label = 'User Input';
      style = filled;
		  color = coral;

      ID [label = 'Student ID']
      KW [label = 'Selected Key Words']
      CS [label = 'Selected Courses']
      }

      subgraph cluster_model_fitting{
      label = 'Model Fitting';
      style = filled;
		  color = LavenderBlush;

      TE [label = 'Topic Expertise']
      AP [label = 'Academic Performance']

      PM [label = 'Predictive Models']
      x1 [shape = circle, width = .01, height = .01, label = '']
      TM [label = 'Topic Model']

@@

      subgraph cluster_inter_last{
      label = 'Intermediate Results';
      style = filled;
		  color = Tan;

      GP [label = 'Grade Prediction']
      AI [label = 'Student´s Academic Interests']
      }

      # Ouput
      subgraph cluster_ouput {
      label = 'System Output';
      style = filled;
		  color = lightCyan;

      SUG [label = 'Course Suggestions']
      WAR [label = 'Warnings']
      PRE [label = 'Preparatory Coursework']
      }

      TR [label = 'Student´s Transcript']

      # Invisible node
      x2 [shape = circle, width = .01, height = .01, label = '']
      x3 [shape = circle, width = .01, height = .01, label = '']

@@

      SD -> AP [weight = 2];
      {SD, TM} -> TE;
      {TM, KW} -> AI;
      ID -> TR;
      {PM, CS, TR} -> GP;
      GP -> WAR;
		  WAR -> PRE;

      CD -> TM [label = '  LDA'];

      {AP, TE} -> x1 [arrowhead = none]
      x1 -> PM [label = '  Lasso'];

      {TM, AI} -> x2 [arrowhead = none]
      x2 -> SUG [label = '  KL distance'];

      {TM, PM} -> x3 [arrowhead = none]
      x3 -> PRE [label = '  KL distance'];

@@

  labs(title = "Model Selection", subtitle = str_c("The maximum-likelihood model has ", max_LL, " topics"), x = "Number of Topics", y = "Log-Likelihood") +
